Long-form recording of infant body position in the home using wearable inertial sensors

### 2023-03-28 manuscript.Rmd
updated author note

  This work was funded by National Science Foundation Grant BCS #1941449 to the first author.

@@

keywords          : "body position, motor development, everyday experiences, sitting, machine learning"
wordcount         : "12,022"

@@

Three online repositories contain openly shared data, materials, and analysis code. A Databrary repository (https://nyu.databrary.org/volume/1580) includes an exemplar participant's recording session, with the raw video data files, the Datavyu annotations of those video files, a log file with machine-readable synchronization points and nap/diaper change times, and accelerometer and gyroscope data for each of the 4 sensors. A GitHub repository (https://github.com/JohnFranchak/body_position_classification_ms.git) contains the exemplar participant's data and source code to: 1) synchronize IMU and video annotations, 2) calculate windowed motion features for their data, and 3) train and test the body position classifier using an "individual model". The chosen participant's classification accuracy was at the median level. Because of the overall size of the full dataset and the computational power/time required to synchronize and create windowed datasets for each session, it would not be feasible to reproduce the calculations for all 34 sessions. However, in a second Github repository (https://github.com/JohnFranchak/body_position_classification_ms.git) we share the full results of those computations: The dataset of windowed motion features with corresponding body position codes used to validate the method (described in the results below), along with the processed intermediary files used for each set of analyses. This reproducible manuscript created in RMarkdown and *papaja* [@papaja] can be regenerated from those data files for full computational transparency.

@@

```{r results="hide"}
devtools::session_info() %>% jsonlite::write_json("session_info.json")
```

>>>>

  This work was funded by National Science Foundation Grant BCS #1941449 to the first author. The authors declare no conflict of interest.

@@

keywords          : "body position, motor development, everyday experiences, sitting, machine learning"
wordcount         : "11,995"

@@

Three online repositories contain openly shared data, materials, and analysis code. A Databrary repository (https://nyu.databrary.org/volume/1580) includes an exemplar participant's recording session, with the raw video data files, the Datavyu annotations of those video files, a log file with machine-readable synchronization points and nap/diaper change times, and accelerometer and gyroscope data for each of the 4 sensors. A GitHub repository (https://github.com/JohnFranchak/body_position_classification_example) contains the exemplar participant's data and source code to: 1) synchronize IMU and video annotations, 2) calculate windowed motion features for their data, and 3) train and test the body position classifier using an "individual model". Because of the overall size of the full dataset and the computational power/time required to synchronize and create windowed datasets for each session, it would not be feasible to reproduce the calculations for all 34 sessions. However, in a second Github repository (https://github.com/JohnFranchak/body_position_classification_ms) we share the full results of those computations: The dataset of windowed motion features with corresponding body position codes used to validate the method. This reproducible manuscript created in RMarkdown and *papaja* [@papaja] can be regenerated from those data files for full computational transparency.

@@

```{r results="hide"}
writeLines(capture.output(devtools::session_info()), "session_info.txt")
```

### 2023-03-28 manuscript.tex
updated author note

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{body position, motor development, everyday experiences, sitting, machine learning\newline\indent Word count: 12,022}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\raggedbottom
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Long-form recording of infant body position in the home using wearable inertial sensors},
  pdfauthor={John M. Franchak1, Maximilian Tang1, Hailey Rousey1, \& Chuan Luo1},
  pdflang={en-EN},
  pdfkeywords={body position, motor development, everyday experiences, sitting, machine learning},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

This work was funded by National Science Foundation Grant BCS \#1941449 to the first author.

@@

Three online repositories contain openly shared data, materials, and analysis code. A Databrary repository (\url{https://nyu.databrary.org/volume/1580}) includes an exemplar participant's recording session, with the raw video data files, the Datavyu annotations of those video files, a log file with machine-readable synchronization points and nap/diaper change times, and accelerometer and gyroscope data for each of the 4 sensors. A GitHub repository (\url{https://github.com/JohnFranchak/body_position_classification_ms.git}) contains the exemplar participant's data and source code to: 1) synchronize IMU and video annotations, 2) calculate windowed motion features for their data, and 3) train and test the body position classifier using an ``individual model''. The chosen participant's classification accuracy was at the median level. Because of the overall size of the full dataset and the computational power/time required to synchronize and create windowed datasets for each session, it would not be feasible to reproduce the calculations for all 34 sessions. However, in a second Github repository (\url{https://github.com/JohnFranchak/body_position_classification_ms.git}) we share the full results of those computations: The dataset of windowed motion features with corresponding body position codes used to validate the method (described in the results below), along with the processed intermediary files used for each set of analyses. This reproducible manuscript created in RMarkdown and \emph{papaja} (Aust \& Barth, 2022) can be regenerated from those data files for full computational transparency.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{body position, motor development, everyday experiences, sitting, machine learning\newline\indent Word count: 11,995}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\raggedbottom
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Long-form recording of infant body position in the home using wearable inertial sensors},
  pdfauthor={John M. Franchak1, Maximilian Tang1, Hailey Rousey1, \& Chuan Luo1},
  pdflang={en-EN},
  pdfkeywords={body position, motor development, everyday experiences, sitting, machine learning},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

This work was funded by National Science Foundation Grant BCS \#1941449 to the first author. The authors declare no conflict of interest.

@@

Three online repositories contain openly shared data, materials, and analysis code. A Databrary repository (\url{https://nyu.databrary.org/volume/1580}) includes an exemplar participant's recording session, with the raw video data files, the Datavyu annotations of those video files, a log file with machine-readable synchronization points and nap/diaper change times, and accelerometer and gyroscope data for each of the 4 sensors. A GitHub repository (\url{https://github.com/JohnFranchak/body_position_classification_example}) contains the exemplar participant's data and source code to: 1) synchronize IMU and video annotations, 2) calculate windowed motion features for their data, and 3) train and test the body position classifier using an ``individual model''. Because of the overall size of the full dataset and the computational power/time required to synchronize and create windowed datasets for each session, it would not be feasible to reproduce the calculations for all 34 sessions. However, in a second Github repository (\url{https://github.com/JohnFranchak/body_position_classification_ms}) we share the full results of those computations: The dataset of windowed motion features with corresponding body position codes used to validate the method. This reproducible manuscript created in RMarkdown and \emph{papaja} (Aust \& Barth, 2022) can be regenerated from those data files for full computational transparency.
